Artigo 1

### 2009-04-22 trunk/latex/artigo1/artigo1.tex
notas sobre o artigo. bibliografia atualizada.

@@

why you have investigated the question

how it relates to earlier research that has been done in the field

1. Open with two or three sentences placing your study subject in context

2. Follow with a description of the problem and its history, including previous research

3. Describe how your work addresses a gap in existing knowledge or ability (here's where you'll state why you've undertaken this study).

4. State what information your article will address.

@@

>>>>

Kent Beck's sentences: The first states the problem. The second states why the problem is a problem. The third is my startling sentence. The fourth states the implication of my startling sentence.

@@

% why you have investigated the question
% 
% how it relates to earlier research that has been done in the field
% 
% 1. Open with two or three sentences placing your study subject in context
% 2. Follow with a description of the problem and its history, including previous research
% 3. Describe how your work addresses a gap in existing knowledge or ability (here's where you'll state why you've undertaken this study). 
% 4. State what information your article will address.

É difícil obter muitos dados, grandes sistemas. Difícil achar sistema com arquitetura conhecida.

embora existam alguns trabalhos avaliando algoritmos de recuperação de arquitetura, os resultados experimentais não dão pistas sobre por que os algoritmos são bons em uns critérios e ruins em outros, quais são as coisas que influenciam o desempenho do algoritmo.

@@

Trabalhos futuros: explorar métricas de arquitetura, avaliar algoritmos de clustering, considerar outros modelos.
